Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-13 paper.tex
Modified cclib section by clarifying GaussSum (and adding text about it's other useful features!); Added text for QMForge.

In 2006, the Blue Obelisk project cclib~\cite{cclib} was established
with the goal of parsing the output from computational chemistry
programs and presenting it in a standard way so that further analyses
could be carried out independently of the quantum package used to
obtain the results. cclib is a Python library, and
the current version (version 1.0.1)
supports 8 different computational chemistry codes and extracts over
30 different calculated attributes. A related BO project,
GaussSum~\cite{WebGaussSum},
is a GUI that builds on top of cclib to allow predicted properties to
be compared to experimental properties (for example, the calculated
vibrational frequencies and the IR spectrum).

>>>>

In 2006, the Blue Obelisk project cclib~\cite{cclib} was established
with the goal of parsing the output from computational chemistry
programs and presenting it in a standard way so that further analyses
could be carried out independently of the quantum package used to
obtain the results. cclib is a Python library, and
the current version (version 1.0.1)
supports 8 different computational chemistry codes and extracts over
30 different calculated attributes. Two related BO projects build upon 
cclib. GaussSum~\cite{WebGaussSum},
is a GUI that can monitors the progress of SCF and geometry convergences, 
and can plot predicted UV/Vis absorption and infrared spectra from 
appropriate logfiles containing energies and oscillator strengths for easy 
comparison to experimental data. QMForge~\cite{WebQMForge} provides 
a GUI for various electronic structure analyses such as Frenking's charge 
decomposition analysis~\cite{Frenking} and Mulliken or C-squared analyses
on user-defined molecular fragments. QMForge also provides a rudamentary
Cartesian coordinate editor allowing molecular structures to be saved via OpenBabel.
